Analysis and results

### 2020-09-02 analysis/02_clean-data.Rmd
Discretized the Q5.3 block

>>>>

    # *Q5.3*: Here is a list of different types of voluntary organizations. For each organization, indicate whether you are an active member, an inactive member, or not a member of that type of organization:
    # |                                         | Active member | Inactive member | Don't belong |
    # | --------------------------------------- | :-----------: | :-------------: | :----------: |
    # | Church or religious organization        |       •       |        •        |      •       |
    # | Sport or recreational organization      |       •       |        •        |      •       |
    # | Art, music, or educational organization |       •       |        •        |      •       |
    # | Labor union                             |       •       |        •        |      •       |
    # | Political party                         |       •       |        •        |      •       |
    # | Environmental organization              |       •       |        •        |      •       |
    # | Professional association                |       •       |        •        |      •       |
    # | Humanitarian or charitable organization |       •       |        •        |      •       |
    # | Consumer organization                   |       •       |        •        |      •       |
    # | Other organization                      |       •       |        •        |      •       |
    Q5.3_1 = fct_relevel(
      factor(Q5.3_1, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_2 = fct_relevel(
      factor(Q5.3_2, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_3 = fct_relevel(
      factor(Q5.3_3, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_4 = fct_relevel(
      factor(Q5.3_4, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_5 = fct_relevel(
      factor(Q5.3_5, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_6 = fct_relevel(
      factor(Q5.3_6, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_7 = fct_relevel(
      factor(Q5.3_7, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_8 = fct_relevel(
      factor(Q5.3_8, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_9 = fct_relevel(
      factor(Q5.3_9, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")
    Q5.3_10 = fct_relevel(
      factor(Q5.3_10, labels = c("Active member", "Inactive member", "Don't belong")), 
      c("Don't belong", "Inactive member", "Active member")

### 2020-09-02 analysis/03_analysis.Rmd
Discretized the Q5.3 block

# Plot marginals

```{r plot-marginals}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 1                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

>>>>

# Plot marginals and contrasts

```{r plot-marginals}
#########

# Update covariate labels
# Add contrasts where appropriate (see hypotheses Rmd documents)

#########

intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 1                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics
